DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-03-04 rebuttal.tex

We share the opinion of the reviewer when he says that 2D CNNs should probably work as well as DeepSphere, ``by taking in a projected 2D image of the sky and using *loads* of filters to learn about the distortion at different parts of the projected sky.'' Hence we decided to add a new experiment in the paper.

Nevertheless, making a comparison is technically not as trivial as it may seems. 
Problematically a radial projection is computationally expensive to the point where, because of the dataset augmentation, it becomes significantly more expensive than the actual training of the network.
Hence, we decided to use the geometrical properties of HEALPix to create a ``special'' projection. 
In the HEALPix sampling, the sphere is first separated into $12$ parts that are then subdivided into $4$ recursively.
Eventually, each of these $12$ part resembles a square grid. 
As the problem we are solving only involve one of these 12 parts, we can use this natural structure to simply re-assign each HEALPix pixel to one of a 2 dimensional grid of size $N_{sides} \times N_{sides}$. 
This operation is computationally very cheap and probably spread quite evenly across the resulting image. 
This projection has recently been used for a CNN in cosmology in the very recent work \cite{krachmalnicoff2019convolutional}.

As we believe that this projection is the optimal one to use a traditonal CNN for application, we performed the experiment using it.

Our expectation were similar with the one of the reviewer, but the results did surprise us as the performance of the traditional CNN did in general not match DeepSphere, (see Figure 9 of the manuscript).
It can probably be explained by the fact that 2DCNN breaks the rotational invariance of the data. 
The problem comes from the fact that the projection introduce a distortion in the geometry and the network has to learn a correct weighting scheme to compensate for it. 
Unfortunately, this operation waste many parameters, reducing the modelization power of the network and requires large amount of training data which is not fully available.
Note that, when visualizing the learned convolution kernels, we observed that they were not radial.

@@

% \mdeff{Agreed that we should do at least one thing they asked for.
% \begin{itemize}
% 	\item Testing on the 1/12 of the sphere is not what he asked for. On one hand, a global projection would exhibit more distortion. On the other, we never use the whole sphere.
% 	\item Keep in mind that there is no orientation that is consistent for the 12 base faces (i.e., where is up?).
% 	\item Agreed that the performance should be very similar. Both are doing local computations. And locally (3 to 5 pixels across), the sphere is isomorphic to an Euclidean plane.
% 	\item The only difference, in my opinion, would be due to the anisotropic filters the 2D CNN has access to.
% 	\item Not sure we should include this result in the main paper. Hard to justify in the story, especially as a comparison with alternative spherical CNNs is missing. Let's see the results.
% \end{itemize}
% }

\subsection{}

\begin{mdframed}[style=comment]
Similarly, I think it would useful to check how well the DeepSphere CNN does against the FCN when the input data is rotated randomly during training - I imagine that the results should match or probably exceed the FCN results and I think this would be a neat little test which doesn't involve needing extra data, just more augmentation.
\end{mdframed}

% That comparison is not warranted.
% or justified. pointless is maybe too aggressive
We do not believe this comparizon is useful because of the following theoretical reason
There are two ways to deal with symmetries one wants to be invariant to: (i) build them into the architecture of the model, or (ii) augment the dataset such that a (more general) model learns them ``brute-force''.
With respect to rotation invariance, the FCN architecture is of the first kind, while the CNN is of the second kind.
Assuming the task is truly invariant to said symmetry,\footnote{As argued in the introduction, cosmological maps are rotation invariant.} the performance of the first kind of models would be exactly the same as without augmentation, while the second kind would only catch up after seeing enough data to learn the invariance.
% That is a waste of resources which is only justified if it's not possible to back the desired invariance in the architecture.
Augmentation is only justified if it's not possible to back the desired invariance in the architecture.
% The reviewer himself makes that point in comment 2.8: ``building a NN to suit your purposes''.
We updated the manuscript to more precisely reflect this argumentation.

\TK{Seems a bit strong to me.. maybe we would write it in a softer language?}
\nati{Now it is OK. But is it still strong enough. We should only point reviewer incoherence if necessary.}

@@

- Could you add a plot comparing the graph Laplacian as a function of number of pixels and the Laplace-Beltrami operator so the reader can explicitly see the convergence?
\end{mdframed}

Good point.
To experimentally show convergence, we would need to build a series of graph Laplacians that converges to the Laplace-Beltrami operator.
This is complicated and requires to solve the theoretical problem first.
Hence, we built one Laplacian and observed some similarities between the two operators instead.
We agree that our wording was unfortunate and have modified the manuscript to mean that we empirically observed a strong correspondence rather than a proper convergence.
The convergence (or even exact correspondence) is a problem we are currently investigating and plan to release as a separate contribution.
See also comment 1.4 and our answer there.

\todo{the new figure A.12 is maybe a weak proof of convergence}

\mdeff{@nati, what do you think?} \nati{I like it. I totally agree with the new wording.}

@@

\subsection{}
\begin{mdframed}[style=comment]
In Appendix C. is there a connection between $t$ and $\sigma$ that you can make, or do you just fit them to be similar? If you just fit them to be similar I'm not sure where the relative differences come from. If they are related, however, then the relative differences make sense, but I can't see what the connection is.
\end{mdframed}

In the current version of the manuscript and the code, we simply fitted a few $t$ to match the different $\sigma$. In theory, there should be a connection between the two values providing the graph Laplacian has converged toward the Laplace Beltrami operator. Again, this is left for a futur contribution.

\subsection{}
\begin{mdframed}[style=comment]
A question that I would like to know personally, are you thinking about a future upgrade to non-radial kernels?
\end{mdframed}
We are thinking about it. However, as the graph framework we are using only works with radial filters, it is not a simple question. One simple trick to make the network sensitive to direction is to add a per-channel fully connected layers. We are currently investigating other potential graph techniques that would lead to non-radial kernels.

\subsection{Details}
\begin{mdframed}[style=comment]
Finally, I noticed a few points in the text where there were typos or things which were difficult to follow and I have put a note of them below and tried to correct them as much as I can so that you don't have to put too much effort in - I can't wait to see this paper published. Sorry that the list is so extensive (I'm a bit of a stickler for details and trying to write papers concisely):
\end{mdframed}
Thank you very much for taking the time for making these corrections. We find them very helpful and improving the quality of the paper.
We implemented most of them, see below.

@@

\begin{mdframed}[style=comment]
Convolutional Neural Networks (CNNs) have been proposed as an alternative analysis tool in cosmology thanks to their ability to automatically design relevant statistics to maximise the precision of the parameter estimation [9–16].

- There are many of us in the community who are not overly keen on "precision" of parameter estimation being the target for machine learning. Rather, we would prefer robustness of parameter estimation. It might be worth changing this sentence a bit so as not to upset some of the referenced authors ;)
\end{mdframed}
\todo{Assigned: @tomek}
\TK{not sure what do to here.. will people get upset? "Precision" is commonly used in cosmology}

\begin{mdframed}[style=comment]
When you have multiple = in equations could you split them on to separate lines? This would make the logical steps for following the equations a lot clearer.
\end{mdframed}
Thank you for the suggestion, normally we would adopt it, but the paper is already quite long, and breaking up the lines in equations would make it even longer. So we decided against it.

\begin{mdframed}[style=comment]
You change a lot between "node", "vertex" and "pixel". Could you stick to one of these? I think that "vertex" or "pixel" makes the most sense ("pixel" due to the HEALPix pixelisation of the maps or vertex because of the use of the $v$ notation). Node is quite confusing in several places because there is an inherent connection between node and neuron in ML literature, and since there is swapping between the three different terms it's a little hard to keep track.
\end{mdframed}
We agree with the reviewer that using different term for the same notion can be confusing for the reader. 
Nevertheless, while ``a node'' and ``a vertex'' are synonyms refering to a graph part, ``a pixel'' is a different concept refering to a point of the (spherical) sampling.
As a result, we decided to keep the ``vertex'' and ``pixel''.
% \todo{Assigned: @all}
% \nati{What do you think? This avoid repetition. But we could be more consistent...}
% \TK{Agreed. Do you want to make the change @nati?}

@@

\begin{mdframed}[style=comment]
In Appendix C. you talk about Kroneker a lot, but earlier you talk about Kroneker $\delta$ (which is it's correct name). It's probably worth sticking with the full name.
\end{mdframed}
We have modified the manuscript according to the reviewer suggestion.

\begin{mdframed}[style=comment]
Sky maps are rotation invariant: rotating maps on the sphere doesn’t change their interpretation, as only the statistics of the maps are relevant.
- I think that you mean that rotating maps on the sphere doesn't change their interpretation *when* only the statistics of the maps are relevant. Say you wanted to compare the NGC against the SGC, then rotating the map would obviously change the results.
\end{mdframed}
This sentence has been reformulated as:
\begin{mdframed}[style=manuscript]
We consider the sky maps rotational invariant as in our case rotating maps on the sphere doesn't change their interpretation since only the statistics of the maps are relevant.
\end{mdframed}

\begin{mdframed}[style=comment]
The flexibility of modelling the data domain with a graph allows to easily model data that spans only a part of the sphere, or data that is not uniformly sampled.

- I think you're missing a "one" after allows. "The flexibility of modelling the data domain with a graph allows one to easily model data that spans only a part of the sphere, or data that is not uniformly sampled."
\end{mdframed}
Thank you for the suggestion, we updated the text.

### 2019-03-04 scnn.tex
some modification

Before doing any numerical analysis on the sphere, one first has to choose a tessellation, i.e., an exhaustive partition of the sphere into finite area elements, where the data under study is quantized.
The simplicity of the spherical form belies the intricacy of global analysis on the sphere: there is no known point set that achieves the analogue of uniform sampling in Euclidean space.
% and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions.
%Any existing proposition of practical schemes for the discrete treatment of such functions on the sphere introduces some systematic error dependent on the global properties of the point set.
While our method is applicable to any pixelisation of the sphere, two details depend on the chosen sampling: (i) the choice of neighbours in the construction of the graph, and (ii) the choice of parent nodes when coarsening the graph.
As HEALPix~\citep{gorski2005healpix} is our target application, we tailor the method to that particular sampling in the subsequent exposition.
\figref{example_maps} shows three examples of HEALPix maps: the Cosmic Microwave Background \citep{planck2015overview}, galaxies found in Sloan Digital Sky Survey Data Release 14 \citep{abolfathi2017sdssDR14}, and an example simulated mass map on the footprint of Dark Energy Survey Data Release 1 \citep{des2018dr1}.

@@

From the HEALPix pixelization, we build a weighted undirected graph $\G = (\V, \E, \W)$, where $\V$ is the set of $N_{pix} = |\V|$ nodes, $\E$ is the set of edges, and $\W$ is the weighted adjacency matrix.
In our graph, each pixel $i$ is represented by a node (also called vertex) $v_i \in \V$.
Each node $v_i$ is then connected to the $8$ (or $7$)\footnote{\label{neighbors}The $12 \times 4 = 48$ pixels at the corner of each rhombus of the base dodecahedron only have 7 neighboring pixels. See Figures~\ref{fig:healpix_graph_4} and~\ref{fig:pooling}.} nodes $v_j$ which represent the neighboring pixels $j$ of pixel $i$, forming edges $(v_i, v_j) \in \E$. Given those edges, we define the weighted adjacency matrix $\W \in \R^{N_{pix} \times N_{pix}}$ as
\begin{equation*}
	\W_{ij} = \begin{cases}
		\exp \left( -\frac{\|\x_i-\x_j\|_2^2}{\rho^2} \right) & \text{if pixels $i$ and $j$ are neighbors,} \\
		0 & \text{otherwise,} \\
	\end{cases}
\end{equation*}
where $\x_i$ is a vector encoding the 3-dimensional coordinates of pixel $i$, and
\begin{equation*}
	\rho = \frac{1}{|\E|} \sum_{(v_i, v_j) \in \E} \|\x_i-\x_j\|_2
\end{equation*}
is the average Euclidean distance over all connected pixels. This weighting scheme is important as distances between pixels are not equal.
Other weighting schemes are possible. For example,~\cite{khasanova2017graphomni} uses the inverse of the distance instead. We found out that the one proposed above works well for our purpose, and did not investigate other approaches, leaving it to future work.
\figref{healpix_graph_4} shows a graph constructed from the HEALPix sampling of a sphere.

@@

Following~\cite{shuman2013emerging}, the normalized graph Laplacian,
defined as $\L = \I - \D^{-1/2} \W \D^{-1/2}$, is a second order differential operator
that can be used to define a Fourier basis on the graph. Here $\D$ is the diagonal
matrix where $\D_{ii} = \b{d}_i$ and $\b{d}_i = \sum_j \W_{ij}$ is the weighted degree of node $v_i$. By construction, the Laplacian is symmetric positive
semi-definite and hence can be decomposed as $\L = \U \bLambda \U\trans$, where $\U = [\b u_1, \ldots, \b u_{N_{pix}}]$ is an
orthonormal matrix of eigenvectors and $\bLambda$ is a diagonal matrix of
eigenvalues. The graph Fourier basis is defined as the Laplacian eigenvectors, motivated by the fact that a Fourier basis should diagonalize the Laplacian operator.
The graph Fourier transform of a signal $\f \in \R^{N_{pix}}$ is simply its projection on the eigenvectors given by
$\hat{\f} = \mathcal{F}_\G \{\f\} = \U\trans \f$. It follows that the inverse graph Fourier transform reads $\mathcal{F}^{-1}_\G \{\hat{\f}\} = \U\hat{\f} = \U \U\trans \f = \f$.
Note that the Fourier modes are ordered in the increasing order of the Laplacian eigenvalues $\bLambda$, which can be interpreted as squared frequencies.
Indeed,
\begin{equation*}
	\bLambda_{ii} = \b u_i\trans \L \b u_i = \sum_{(v_j, v_k) \in \E} \frac{\W_{jk}}{\sqrt{\b d_j \b d_k}} (\U_{ji} - \U_{ki})^2
\end{equation*}
is a measure of the variation of the eigenvector $\b u_i$ on the graph defined by the Laplacian $\L$.

@@

Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph. It can however be \textit{localized} on any vertex $v_i$ by the convolution with a Kronecker delta\footnote{A Kronecker delta is the signal $\b \delta^i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} $\b \delta^i \in \R^{N_{pix}}$. The localization operator $\T_i$ reads $\T_i h = h(\L) \b \delta^i = (h(\L))_i$, the $i$th column of $h(\L)$.
This localization of the kernel $h$ can be useful to visualize kernels, as shown in an example of heat diffusion presented in~\ref{sec:filter_visualization}.
If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another. While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular. However, when considering only parts of the sphere, one can observe important border effects (see ~\ref{sec:border_effects}).

@@

Fortunately, both of these computational issues are overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parametrised by $K+1$ coefficients $\theta$.
The filtering operation \eqnref{graph_convolution_fourier} becomes
\begin{equation} \label{eqn:graph_convolution_monomial}
	h_\theta(\L) \f =  \U \left(\sum_{k=0}^K \theta_k \bLambda^k \right) \U\trans \f = \sum_{k=0}^K \theta_k \L^k \f,
\end{equation}
where $\L^k$ captures $k$-neighborhoods.\footnote{The 1-neighborhood of a node is the set of nodes that are directly connected to it. The $k$-neighborhood of a node is the set of nodes that are connected to it through paths of length $k$.}
The entry $(\L^k)_{ij}$ is the sum of all weighted paths of length $k$ between nodes $v_i$ and $v_j$, where the weight of a path is the multiplication of all the edge weights on the path.
Hence, it is non-zero if and only if nodes $v_i$ and $v_j$ are connected by at least one path of length $k$.
Filtering with a polynomial convolution kernel can thus be interpreted in the pixel (vertex) domain as a weighted linear combination of neighboring pixel values.
In the classical setting, convolutions are also weighted local sums.
The weights are however given by the filter coefficients only, and there is one coefficient per pixel in the patch.
In the graph setting, the weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$, and there is one coefficient per neighborhood, not node.
That defines radial filters, values of which depend only on the distance to the center, and not on the direction.
% It is required as there is no way to order and match nodes from the same neighborhood.
% The number of nodes in a neighborhood most often even vary from node to node.
While it may seem odd to restrict filters to be 1D while the sphere is 2D, radial filters are direction-less and result in rotation equivariant convolutions.
We note that restricting the graph convolutional kernel to a polynomial is similar to restricting the classical Euclidean convolution to a fixed-size patch.
Similarly, each column of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an irregular patch of radius $K$.
Hence, filters designed as polynomials of the Laplacian have local support in the vertex domain.

@@

Coarsening can be naturally designed for hierarchical pixelisation schemes, where each subdivision divides a cell in an equal number of child sub-cells.
% Coarsening is the reverse operation: merging the sub-cells toward the goal of summarizing the data supported on them.
To coarsen, the sub-cells are merged to summarise the data supported on them.
Merging cells lead to a coarser graph.
Coarsening defines $\C(i)$, the set of children of node $v_i$.
For the HEALPix subdivision scheme, the number of children is constant, i.e., $| \C(i) | = 4^p \ \forall i$, for some $p$.

@@

Given a matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$, a $GC$ layer computes $\Y = GC(\X) = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels (and nodes), $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
Using the efficient graph convolution from \eqnref{graph_convolution_cheby}, each output feature map is computed as
\begin{equation*}
	\y_i = \sum_{j=1}^{F_{in}} h_{\theta_{ij}}(\tL) \x_j + b_i \in \R^{N_{pix}}, \ \ \forall i \in [F_{out}].
\end{equation*}
As such, a $GC$ layer is composed of $F_{in} \times F_{out}$ filters, each parameterized by $K$ numbers (see \secref{efficient_convolution}). A bias term $\b b \in \R^{F_{out}}$ is jointly optimized.

@@

There are in general two ways to deal with symmetries one wants to be invariant to: (i) build them into the architecture, or (ii) augment the dataset such that a (more general) model learns them.
With respect to rotation invariance, the FCN architecture is of the first kind, while the CNN is of the second kind.
For tasks that are rotation invariant, FCNs hence need less training data as the rotation symmetry is backed in the architecture and need not be learned.
This can be seen as intrinsic data augmentation, as a CNN would need to see many rotated versions of the same data to learn the invariance.
Moreover, FCNs can accommodate maps with a varying number of pixels.
% agnostic to the size of the input data, i.e., it can classify maps which do not have the same number of pixels.
Such global summarization as the $AV$ layer is commonly used along graph convolutions to classify graphs of varying sizes (as it is invariant to node permutation) \citep{duvenaud2015gcn, li2015gatedgnn}.
As such, CNNs should only be used if rotation invariance is undesired.

@@

\begin{figure}[t!]
    \centering
    \includegraphics[height=7em]{sphere_grid_equirectangular}
    \hfill
    \includegraphics[height=7em]{sphere_grid_cubedsphere}
    \hfill
    \includegraphics[height=7em]{half_graph_4}
    \caption[]{Some pixelizations of the sphere. Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system. Middle: an equiangular cubed-sphere grid, as described in \citep{ronchi1996cubed}. Right: graph built from a HEALPix pixelization of half the sphere ($N_{side} = 4$). By construction, each node has eight neighbors, except the highlighted ones which have only seven.\footnotemark[4] Left and middle figures are taken from \citep{boomsma2017spherical}.}
    \label{fig:sphere_grids}
    \label{fig:healpix_graph_4}
\end{figure}

@@

In \figref{gaussian_filters_visualization}, we further leverage this example to present the three visualizations of a HEALPix graph convolution kernel.
We remember that the convolution kernel resulting from the heat diffusion is defined as $K_t(x)=e^{-\tau t x}$. For our (top) visualization, we simply plot this function, i.e., we evaluate $K_t$
at the graph eigenvalues $\text{diag}(\bLambda)$. Note that, the lower eigenvalues $\lambda$ correspond to the lower frequencies, i.e., the spectral mode with less variation.
As a second visualization (middle), we observe the kernel directly on the sphere. As the kernel $K_t$ is defined in the graph spectral domain, we convolve a Kroneker $\delta$  to obtain a representation on the sphere. We then plot the result with a gnomonic projection.
\nati{For our third visualization (bottom), our goal is to plot the section of a filter. This visualization might be convenient as we theoretically have spherical filters (up to the irregularities of the sampling). The idea is to plot the section of the convolved Kroneker $\delta$.}
To do so, we convolve a Kroneker $\delta$ on the nodes along the equator and use the equator for our section.
Note that, because of the small irregularities in the HEALPix sampling, the second and the third methods are subject to small variations depending on the chosen position of the Kroneker $\delta$ .

>>>>

Before doing any numerical analysis on the sphere, one first has to choose a tessellation, i.e., an exhaustive partition of the sphere into finite area elements, where the data under study is quantized.
The simplicity of the spherical form belies the intricacy of global analysis on the sphere: there is no known point set that achieves the analogue of uniform sampling in Euclidean space.
% and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions.
%Any existing proposition of practical schemes for the discrete treatment of such functions on the sphere introduces some systematic error dependent on the global properties of the point set.
While our method is applicable to any pixelisation of the sphere, two details depend on the chosen sampling: (i) the choice of neighbours in the construction of the graph, and (ii) the choice of parent vertices when coarsening the graph.
As HEALPix~\citep{gorski2005healpix} is our target application, we tailor the method to that particular sampling in the subsequent exposition.
\figref{example_maps} shows three examples of HEALPix maps: the Cosmic Microwave Background \citep{planck2015overview}, galaxies found in Sloan Digital Sky Survey Data Release 14 \citep{abolfathi2017sdssDR14}, and an example simulated mass map on the footprint of Dark Energy Survey Data Release 1 \citep{des2018dr1}.

@@

From the HEALPix pixelization, we build a weighted undirected graph $\G = (\V, \E, \W)$, where $\V$ is the set of $N_{pix} = |\V|$ vertices, $\E$ is the set of edges, and $\W$ is the weighted adjacency matrix.
In our graph, each pixel $i$ is represented by a vertex (also called vertex) $v_i \in \V$.
Each vertex $v_i$ is then connected to the $8$ (or $7$)\footnote{\label{neighbors}The $12 \times 4 = 48$ pixels at the corner of each rhombus of the base dodecahedron only have 7 neighboring pixels. See Figures~\ref{fig:healpix_graph_4} and~\ref{fig:pooling}.} vertices $v_j$ which represent the neighboring pixels $j$ of pixel $i$, forming edges $(v_i, v_j) \in \E$. Given those edges, we define the weighted adjacency matrix $\W \in \R^{N_{pix} \times N_{pix}}$ as
\begin{equation*}
	\W_{ij} = \begin{cases}
		\exp \left( -\frac{\|\x_i-\x_j\|_2^2}{\rho^2} \right) & \text{if pixels $i$ and $j$ are neighbors,} \\
		0 & \text{otherwise,} \\
	\end{cases}
\end{equation*}
where $\x_i$ is a vector encoding the 3-dimensional coordinates of pixel $i$, and
\begin{equation*}
	\rho = \frac{1}{|\E|} \sum_{(v_i, v_j) \in \E} \|\x_i-\x_j\|_2
\end{equation*}
is the average Euclidean distance over all connected pixels. This weighting scheme is important as distances between pixels are not equal.
Other weighting schemes are possible. For example,~\cite{khasanova2017graphomni} uses the inverse of the distance instead. We found out that the one proposed above works well for our purpose, and did not investigate other approaches, leaving it to future work.
\figref{healpix_graph_4} shows a graph constructed from the HEALPix sampling of a sphere.

@@

Following~\cite{shuman2013emerging}, the normalized graph Laplacian,
defined as $\L = \I - \D^{-1/2} \W \D^{-1/2}$, is a second order differential operator
that can be used to define a Fourier basis on the graph. Here $\D$ is the diagonal
matrix where $\D_{ii} = \b{d}_i$ and $\b{d}_i = \sum_j \W_{ij}$ is the weighted degree of vertex $v_i$. By construction, the Laplacian is symmetric positive
semi-definite and hence can be decomposed as $\L = \U \bLambda \U\trans$, where $\U = [\b u_1, \ldots, \b u_{N_{pix}}]$ is an
orthonormal matrix of eigenvectors and $\bLambda$ is a diagonal matrix of
eigenvalues. The graph Fourier basis is defined as the Laplacian eigenvectors, motivated by the fact that a Fourier basis should diagonalize the Laplacian operator.
The graph Fourier transform of a signal $\f \in \R^{N_{pix}}$ is simply its projection on the eigenvectors given by
$\hat{\f} = \mathcal{F}_\G \{\f\} = \U\trans \f$. It follows that the inverse graph Fourier transform reads $\mathcal{F}^{-1}_\G \{\hat{\f}\} = \U\hat{\f} = \U \U\trans \f = \f$.
Note that the Fourier modes are ordered in the increasing order of the Laplacian eigenvalues $\bLambda$, which can be interpreted as squared frequencies.
Indeed,
\begin{equation*}
	\bLambda_{ii} = \b u_i\trans \L \b u_i = \sum_{(v_j, v_k) \in \E} \frac{\W_{jk}}{\sqrt{\b d_j \b d_k}} (\U_{ji} - \U_{ki})^2
\end{equation*}
is a measure of the variation of the eigenvector $\b u_i$ on the graph defined by the Laplacian $\L$.

@@

Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph. It can however be \textit{localized} on any vertex $v_i$ by the convolution with a Kronecker delta\footnote{A Kronecker delta is the signal $\b \delta^i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} $\b \delta^i \in \R^{N_{pix}}$. The localization operator $\T_i$ reads $\T_i h = h(\L) \b \delta^i = (h(\L))_i$, the $i$th column of $h(\L)$.
This localization of the kernel $h$ can be useful to visualize kernels, as shown in an example of heat diffusion presented in~\ref{sec:filter_visualization}.
If the graph is not regular, i.e., all vertices do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one vertex to another. While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular. However, when considering only parts of the sphere, one can observe important border effects (see ~\ref{sec:border_effects}).

@@

Fortunately, both of these computational issues are overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parametrised by $K+1$ coefficients $\theta$.
The filtering operation \eqnref{graph_convolution_fourier} becomes
\begin{equation} \label{eqn:graph_convolution_monomial}
	h_\theta(\L) \f =  \U \left(\sum_{k=0}^K \theta_k \bLambda^k \right) \U\trans \f = \sum_{k=0}^K \theta_k \L^k \f,
\end{equation}
where $\L^k$ captures $k$-neighborhoods.\footnote{The 1-neighborhood of a vertex is the set of vertices that are directly connected to it. The $k$-neighborhood of a vertex is the set of vertices that are connected to it through paths of length $k$.}
The entry $(\L^k)_{ij}$ is the sum of all weighted paths of length $k$ between vertices $v_i$ and $v_j$, where the weight of a path is the multiplication of all the edge weights on the path.
Hence, it is non-zero if and only if vertices $v_i$ and $v_j$ are connected by at least one path of length $k$.
Filtering with a polynomial convolution kernel can thus be interpreted in the pixel (vertex) domain as a weighted linear combination of neighboring pixel values.
In the classical setting, convolutions are also weighted local sums.
The weights are however given by the filter coefficients only, and there is one coefficient per pixel in the patch.
In the graph setting, the weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$, and there is one coefficient per neighborhood, not vertex.
That defines radial filters, values of which depend only on the distance to the center, and not on the direction.
% It is required as there is no way to order and match vertices from the same neighborhood.
% The number of vertices in a neighborhood most often even vary from vertex to vertex.
While it may seem odd to restrict filters to be 1D while the sphere is 2D, radial filters are direction-less and result in rotation equivariant convolutions.
We note that restricting the graph convolutional kernel to a polynomial is similar to restricting the classical Euclidean convolution to a fixed-size patch.
Similarly, each column of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an irregular patch of radius $K$.
Hence, filters designed as polynomials of the Laplacian have local support in the vertex domain.

@@

Coarsening can be naturally designed for hierarchical pixelisation schemes, where each subdivision divides a cell in an equal number of child sub-cells.
% Coarsening is the reverse operation: merging the sub-cells toward the goal of summarizing the data supported on them.
To coarsen, the sub-cells are merged to summarise the data supported on them.
Merging cells lead to a coarser graph.
Coarsening defines $\C(i)$, the set of children of vertex $v_i$.
For the HEALPix subdivision scheme, the number of children is constant, i.e., $| \C(i) | = 4^p \ \forall i$, for some $p$.

@@

Given a matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$, a $GC$ layer computes $\Y = GC(\X) = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels (and vertices), $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
Using the efficient graph convolution from \eqnref{graph_convolution_cheby}, each output feature map is computed as
\begin{equation*}
	\y_i = \sum_{j=1}^{F_{in}} h_{\theta_{ij}}(\tL) \x_j + b_i \in \R^{N_{pix}}, \ \ \forall i \in [F_{out}].
\end{equation*}
As such, a $GC$ layer is composed of $F_{in} \times F_{out}$ filters, each parameterized by $K$ numbers (see \secref{efficient_convolution}). A bias term $\b b \in \R^{F_{out}}$ is jointly optimized.

@@

There are in general two ways to deal with symmetries one wants to be invariant to: (i) build them into the architecture, or (ii) augment the dataset such that a (more general) model learns them.
With respect to rotation invariance, the FCN architecture is of the first kind, while the CNN is of the second kind.
For tasks that are rotation invariant, FCNs hence need less training data as the rotation symmetry is backed in the architecture and need not be learned.
This can be seen as intrinsic data augmentation, as a CNN would need to see many rotated versions of the same data to learn the invariance.
Moreover, FCNs can accommodate maps with a varying number of pixels.
% agnostic to the size of the input data, i.e., it can classify maps which do not have the same number of pixels.
Such global summarization as the $AV$ layer is commonly used along graph convolutions to classify graphs of varying sizes (as it is invariant to vertex permutation) \citep{duvenaud2015gcn, li2015gatedgnn}.
As such, CNNs should only be used if rotation invariance is undesired.

@@

\begin{figure}[t!]
    \centering
    \includegraphics[height=7em]{sphere_grid_equirectangular}
    \hfill
    \includegraphics[height=7em]{sphere_grid_cubedsphere}
    \hfill
    \includegraphics[height=7em]{half_graph_4}
    \caption[]{Some pixelizations of the sphere. Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system. Middle: an equiangular cubed-sphere grid, as described in \citep{ronchi1996cubed}. Right: graph built from a HEALPix pixelization of half the sphere ($N_{side} = 4$). By construction, each vertex has eight neighbors, except the highlighted ones which have only seven.\footnotemark[4] Left and middle figures are taken from \citep{boomsma2017spherical}.}
    \label{fig:sphere_grids}
    \label{fig:healpix_graph_4}
\end{figure}

@@

In \figref{gaussian_filters_visualization}, we further leverage this example to present the three visualizations of a HEALPix graph convolution kernel.
We remember that the convolution kernel resulting from the heat diffusion is defined as $K_t(x)=e^{-\tau t x}$. For our (top) visualization, we simply plot this function, i.e., we evaluate $K_t$
at the graph eigenvalues $\text{diag}(\bLambda)$. Note that, the lower eigenvalues $\lambda$ correspond to the lower frequencies, i.e., the spectral mode with less variation.
As a second visualization (middle), we observe the kernel directly on the sphere. As the kernel $K_t$ is defined in the graph spectral domain, we convolve a Kroneker $\delta$  to obtain a representation on the sphere. We then plot the result with a gnomonic projection.
\nati{For our third visualization (bottom), our goal is to plot the section of a filter. This visualization might be convenient as we theoretically have spherical filters (up to the irregularities of the sampling). The idea is to plot the section of the convolved Kroneker $\delta$.}
To do so, we convolve a Kroneker $\delta$ on the vertices along the equator and use the equator for our section.
Note that, because of the small irregularities in the HEALPix sampling, the second and the third methods are subject to small variations depending on the chosen position of the Kroneker $\delta$ .
